Price of Anarchy for Mean Field Games

### 2018-07-24 PoA.tex
update prop 4 finish

\begin{remark}
	It can be seen later in the proof that when $b_2 \to \infty$, both $SC^{MFG}$ and $SC^{MKV}$ tend towards $0$. The idea here becomes to estimate the order of magnitude in terms of $b_2$ for the quantity $\Delta SC$ and $SC^{MKV}$. Indeed, we will show that $\Delta SC$ decreases exponentially fast when $b_2$ tends towards infinity while $SC^{MKV}$ decreases as fast as $1/b_2$. Therefore, the Price of Anarchy $PoA$ will decrease exponentially fast as $b_2 \to \infty$, which can also be observed in the numerical result hereafter. 
\end{remark}

\begin{proof}
	If $\bar{b}_2 = 0$ then 
	$$\lambda = \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}$$ which is a constant independent of $b_2$,
	otherwise when $b_2 \to \infty$, we still have
	$ \lambda^{b_2} \to \lambda^{b_2 \to \infty}$.	
	For other coefficients, in the case when $b_2 \to \infty$ we have 
	\begin{equation*}
	\begin{array}{l}
	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty}
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$.

	Moreover
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}
	\end{equation*}
	Thus we have $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $0 \leq t < T$:
	$$\displaystyle  e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} \xrightarrow[b_2 \to \infty]{} 0.$$
	From the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, we can compute the limit of $(b_2 + \bar{b}_2) u_t^{b_2}$ for any $t \in [0,T)$ by dividing the numerator with $(b_2 + \bar{b}_2)$ and the denominator with $(b_2)+\bar{b}_2)^2$, namely
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u
	\end{IEEEeqnarray*}
	Idem, we can have for any $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} }.$$
%	and for any $t \in [0,T)$,
%	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r+ \bar{r}) c_{\delta_\eta^{b_2 \to \infty}} =: c_5, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{\frac{q+\bar{q}}{r + \bar{r}}}.
%	$$

	Moreover, we can derive a uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ for any large enough $b_2$ by expanding this whole expression with equation (\ref{eq:riccati_ut_sol}). Let $\epsilon_1 > 0$ so that $\epsilon_1 < \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$. Then there exists $b_2^{*,lower}>0$ such that for all $b_2 \geq b_2^{*,lower}$ we have:
	$$ 
	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - (-c_{\delta_u^{b_2 \to \infty}}) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert  \right\} \leq \epsilon_1,
	$$ 
	so that
	\begin{IEEEeqnarray}{rCl}
		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
		&=& \frac{D^{u,b_2} \frac{\delta_u^{+, b_2}}{b_2+ \bar{b}_2} }{ \frac{\delta_u^{+,b_2} - \delta_u^{-,b_2}}{b_2 + \bar{b}_2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \nonumber \\
		&\geq& \frac{(D^{u,b_2 \to \infty} - \epsilon_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \epsilon_1) }{ (2 c_{\delta_u^{b_2 \to \infty}} + 2 \epsilon_1) + (D^{u,b_2 \to \infty} + \epsilon_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)
	\end{IEEEeqnarray}

	% upper bound for u_t, w_t
	Also, from the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, given any fixed $b_2$, we can compute the derivative of $u_t^{b_2}$ with respect to time $t$ and obtain:
	\begin{equation}
		\frac{d u_t^{b_2}}{dt} = \frac{\left(B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \right) \cdot (\delta_u^{+,b_2} - \delta_u^{-,b_2}) e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t) } }{\left[(- \delta_u^{-,b_2} + B^{b_2} D^{u,b_2} )  + (\delta_u^{+,b_2} - B^{b_2} D^{u,b_2} )e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)} \right]^2 }
	\end{equation}
	Hence $t \mapsto u_t^{b_2}$ is increasing when $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
	$$ B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \xrightarrow[b_2 \to \infty]{} \infty,$$
	there must exists $b_2^{*,u,upper}>0$ such that for all $b_2 \geq b_2^{*,u,upper}$ we have $t \mapsto u_t^{b_2}$ being an increasing function and 
	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} \leq \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$
	Idem for $t \mapsto w_t^{b_2}$. Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+1, D^w+1\}$, we have a uniform upper bound for $u_t^{b_2}$ and $w_t^{b_2}$ for all $b_2$ large enough,namely
	\begin{equation}
	\sup_{b_2 \geq b_2^{*,upper}} \sup_{0 \leq t \leq T} \max \left\{ u_t^{b_2} , w_t^{b_2}\right\} \leq M.
	\label{eq:ut_wt_upper_bound_b2_infty}
	\end{equation}

	The next step is to provide an estimation of the order of magnitude of $\Delta SC$ and $SC^{MKV}$. For all $t \in [0,T)$, we denote $h_u(b_2,t) = (b_2 + \bar{b}_2) u_{t}^{b_2}$, $h_w(b_2,t) = (b_2 + \bar{b}_2)w_t^{b_2}$ and $h_\eta(b_2,t) = b_2 \eta_t^{b_2}$.\\

@@

	\begin{comment}
	Idem, there exists 3 time points $t_7,t_8,t_9$ with $0<t_7<t_3<T$ and $0<t_8<t_9<t_3<T$ such that
	\begin{equation}
		v^{b_2}_{t_3} = \kappa_8 e^{-\kappa_7 b_2 h_\eta(b_2,t_7)} + \kappa_{10} e^{-\kappa_9 b_2 h_\eta(b_2,t_9)}
	\label{eq:v_{t_3}_b_2_expansion}
	\end{equation}
	where $ \displaystyle \kappa_7 = \frac{2t_3}{r+ \bar{r}}, \  \kappa_8 =Var(\xi) e^{2b_1 t_3}, \  \kappa_9 = \frac{2 (t_3 - t_8)}{r+ \bar{r}}, \  \kappa_{10}= \sigma^2 t_3 e^{2b_1 (t_3 - t_8)}$.
	\end{comment}

>>>>

%\begin{remark}
%	It can be seen later in the proof that when $b_2 \to \infty$, both $SC^{MFG}$ and $SC^{MKV}$ tend towards $0$. The idea here becomes to estimate the order of magnitude in terms of $b_2$ for the quantity $\Delta SC$ and $SC^{MKV}$. Indeed, we will show that $\Delta SC$ decreases exponentially fast when $b_2$ tends towards infinity while $SC^{MKV}$ decreases as fast as $1/b_2$. Therefore, the Price of Anarchy $PoA$ will decrease exponentially fast as $b_2 \to \infty$, which can also be observed in the numerical result hereafter. 
%\end{remark}

\begin{proof}
	If $\bar{b}_2 = 0$ then 
	$$\lambda = \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}$$ which is a constant independent of $b_2$,
	otherwise when $b_2 \to \infty$ we have
	$ \lambda^{b_2} \to \lambda^{b_2 \to \infty}$.	
	For other coefficients, as long as $b_2 \to \infty$ we have 
	\begin{equation*}
	\begin{array}{l}
	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty}
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$.

	Moreover, we notice that
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
	\end{equation*}
	Thus $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $0 \leq t < T$:
	$$\displaystyle  e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} \xrightarrow[b_2 \to \infty]{} 0.$$
	From the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, we can compute the limit of $(b_2 + \bar{b}_2) u_t^{b_2}$ for any $t \in [0,T)$ by dividing the numerator with $(b_2 + \bar{b}_2)$ and the denominator with $(b_2)+\bar{b}_2)^2$, namely
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u
	\end{IEEEeqnarray*}
	Idem, for any $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} }.$$
%	and for any $t \in [0,T)$,
%	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r+ \bar{r}) c_{\delta_\eta^{b_2 \to \infty}} =: c_5, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{\frac{q+\bar{q}}{r + \bar{r}}}.
%	$$

	% lower bound for (b_2 + b2 bar) u_t
	Moreover, we can derive a uniform lower bound for $(b_2 + \bar{b}_2) u_t^{b_2}$ for any large enough $b_2$ by expanding this whole expression with equation (\ref{eq:riccati_ut_sol}). Let $\epsilon_1 > 0$ so that $\epsilon_1 < \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$, for example $\epsilon_1 = \frac{1}{2} \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}$. Then there exists $b_2^{*,lower} := b_2^{*,lower}(\epsilon_1) 	>0$ such that for all $b_2 \geq b_2^{*,lower}$,
	$$ 
	\max \left\{  \left\vert \frac{\delta_u^{+,b_2}}{b_2 + \bar{b}_2}  - c_{\delta_u^{b_2 \to \infty}} \right\vert, \   \left\vert \frac{\delta_u^{-,b_2}}{b_2 + \bar{b}_2}  - (-c_{\delta_u^{b_2 \to \infty}}) \right\vert, \vert D^{u,b_2} - D^{u,b_2\to \infty} \vert  \right\} \leq \epsilon_1,
	$$ 
	so that
	\begin{IEEEeqnarray}{rCl}
		(b_2 + \bar{b}_2) u_t^{b_2} &\geq&  (b_2 + \bar{b}_2) \frac{D^{u,b_2} \delta_u^{+, b_2} }{ (\delta_u^{+,b_2} - \delta_u^{-,b_2}) + B^{b_2}D^{u,b_2} } \nonumber \\
		&=& \frac{D^{u,b_2} \frac{\delta_u^{+, b_2}}{b_2+ \bar{b}_2} }{ \frac{\delta_u^{+,b_2} - \delta_u^{-,b_2}}{b_2 + \bar{b}_2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \nonumber \\
		&\geq& \frac{(D^{u,b_2 \to \infty} - \epsilon_1 ) \cdot (c_{\delta_u^{b_2 \to \infty}} - \epsilon_1) }{ (2 c_{\delta_u^{b_2 \to \infty}} + 2 \epsilon_1) + (D^{u,b_2 \to \infty} + \epsilon_1) / (r+ \bar{r}(1-\bar{s})^2) } =: m_u(\epsilon_1)
	\label{eq:ut_uniform_lower_bound_b2_infinity}
	\end{IEEEeqnarray}

	% upper bound for u_t, w_t
	Also, from the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, given any fixed $b_2$, we can compute the derivative of $u_t^{b_2}$ with respect to time $t$ and obtain:
	\begin{equation*}
		\frac{d u_t^{b_2}}{dt} = \frac{\left(B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \right) \cdot (\delta_u^{+,b_2} - \delta_u^{-,b_2}) e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t) } }{\left[(- \delta_u^{-,b_2} + B^{b_2} D^{u,b_2} )  + (\delta_u^{+,b_2} - B^{b_2} D^{u,b_2} )e^{- (\delta_u^{+,b_2} - \delta_u^{-,b_2})(T-t)} \right]^2 }.
	\end{equation*}
	Hence, the function $t \mapsto u_t^{b_2}$ is increasing when $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
	$$ B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} \xrightarrow[b_2 \to \infty]{} \infty,$$
	there must exists $b_2^{*,u,upper}>0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ being increasing and 
	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} \leq \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$
	Idem for $t \mapsto w_t^{b_2}$. Let $b_2^{*,upper} = \max \{ b_2^{*,u,upper}, b_2^{*,w,upper}\}$ and $M = \max \{  D^{u,b_2 \to \infty}+1, D^w+1\}$, we get a uniform upper bound for $u_t^{b_2}$ and $w_t^{b_2}$ for all $b_2\geq b_2^{*,upper}$, namely
	\begin{equation}
	\sup_{b_2 \geq b_2^{*,upper}} \sup_{0 \leq t \leq T} \max \left\{ u_t^{b_2} , w_t^{b_2}\right\} \leq M.
	\label{eq:ut_wt_upper_bound_b2_infty}
	\end{equation}

	Now we are ready to show that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. The idea is to split the whole interval into two parts $[0,T] =[0,t^*] \cup [t^*,T]$.	
	Since $v_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV} \geq w_0^{b_2} \mathbb{E}(\xi)^2$.	For the sake of simplicity, for all $t \in [0,T]$, we denote $h_u(b_2,t) = (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) = (b_2 + \bar{b}_2)w_t^{b_2}$. Thus by multiplying $(b_2 + \bar{b}_2)$ both on the numerator and denominator we get
	\begin{IEEEeqnarray*}{rCl}
		0 \leq \frac{\Delta SC}{SC^{MKV}} &\leq& \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{[0,t^*]} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{[t^*, T]} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\ 
		&=&  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1 + I_2 \right)
	\end{IEEEeqnarray*}
	where
	\begin{IEEEeqnarray*}{rCl}
	I_1 &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{t^*} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
	\right) dt \\
	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{t^*} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt	 
	\end{IEEEeqnarray*}
	and 
	$$
		I_2 = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{t^*}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
	$$	
	The time point $t^*$ is chosen afterwards in order to make $I_1$ small enough. For any given $\epsilon>0$, we want to show that $I_1 \leq \epsilon$ and $I_2 \leq \epsilon$ for any $b_2$ large enough.\\

	% the term I_1
	We look at the term $I_1$ first. Recall that on the closed sub-interval $[0,T/2]$, we have pointwise convergence $(b_2 + \bar{b}_2) u_t^{b_2} \to c_u$ and $(b_2 + \bar{b}_2) w_t^{b_2} \to c_w$. Because we have shown that for all $b_2 \geq b_w^{*,upper}$, the functions $[0,T/2] \ni s \mapsto u_s^{b_2}$ and $[0,T/2] \ni s \mapsto w_s^{b_2}$ are increasing. Consequently, for any positive constant $\epsilon_2 < \min \{ c_u, c_w \} $, saying for example $\epsilon_2 = \frac{1}{2} \min \{c_u, c_w \}$, there exists $b_2^{*,I_1} := b_2^{*,I_1}(\epsilon_2) > b_2^{*,upper}$ such that for all $b_2 \geq b_2^{*,I_1}$ and all $s\in [0, T/2]$ we have:
	\begin{equation*}
	\left\{
	\begin{array}{lclclclcl}
		c_u - \epsilon_2 &\leq& h_u(b_2,0) &\leq& h_u(b_2,s) &\leq& h_u(b_2, T/2 ) &\leq& c_u + \epsilon_2 \\
		c_w - \epsilon_2 &\leq& h_w(b_2,0) &\leq& h_w(b_2,s) &\leq& h_w(b_2, T/2 ) &\leq& c_w + \epsilon_2 
	\end{array}
	\right.
	\end{equation*}
	Thus, if $t^* < \frac{T}{2}$, then for any $t \in [0,t^*] \subset [0,T/2]$ and $b_2 \geq b_2^{*,I_1}$,
	$$
		\vert h_u(b_2, t) - h_w(b_2,t) \vert^2 \leq  2 [ (c_u + \epsilon_2)^2 + (c_w+ \epsilon_2)^2 ]\quad \text{and} \quad \int_0^t h_u(b_2,s)ds \geq (c_u - \epsilon_2) t,
	$$
	which implies
	\begin{IEEEeqnarray}{rCl}
		I_1 &=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{t^*} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt \nonumber \\
		&\leq& \frac{e^{(b_1 + \bar{b}_1) T}\cdot  2[ (c_u+ \epsilon_2)^2 + (c_w + \epsilon_2)^2 ]}{r+ \bar{r}(1-\bar{s})^2} \cdot (b_2 + \bar{b}_2) \int_0^{t^*} \exp \left(  - \frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \cdot (c_u - \epsilon_2) t \right) dt \nonumber \\
		&=& \kappa_1 \left( 1 - e^{ - \kappa_2 \cdot (b_2 + \bar{b}_2) t^* } \right) 
	\label{eq:I1_ineq_b2_infinity}
	\end{IEEEeqnarray}
	where the coefficients $ \displaystyle \kappa_1 := \kappa_1(\epsilon_2) = \frac{e^{(b_1 + \bar{b}_1) T}\cdot  [ (c_u+ \epsilon_2)^2 + (c_w + \epsilon_2)^2 ]}{c_u - \epsilon_2}$ and $\displaystyle \kappa_2 := \kappa_2(\epsilon_2) = \frac{2 (c_u - \epsilon_2)}{r + \bar{r}(1-\bar{s})^2} $ independent of $b_2$.	
	In particular, the above inequality is valid when $b_2 = b_2^{*,I_1}$, so if we let $\epsilon_2 = \frac{1}{2} \min \{c_u, c_w\}$ as previous, and choose the time point $t^*$ as following
	\begin{equation}
	 t^* := t^*(\epsilon) = \min\left\{ \frac{T}{2}, \  \frac{1}{\kappa_2 \cdot \left( b_2^{*,I_2} + \bar{b}_2\right) } \ln \left( \frac{1}{\displaystyle 1- \frac{\epsilon}{\kappa_1} } \right) \right\},
	\label{eq:t^*_b2_infty} 
	\end{equation}
	then we are able to deduce from inequality (\ref{eq:I1_ineq_b2_infinity}) that
	\begin{equation}
		I_1 \leq \kappa_1 \left[1 - e^{- \kappa_2 \cdot (b_2^{*,I_2} + \bar{b}_2) \cdot t^*}  \right] = \epsilon.\\
	\label{eq:I1_b2_infty}
	\end{equation}

	% check I_2
	Now we look at the term $I_2$ with the above given $t^*(\epsilon)$. 
	Since the functions $s \mapsto u_s^{\bar{b}_2}$, $s \mapsto w_s^{\bar{b}_2}$ and $s \mapsto \bar{x}_s^{MFG,\bar{b}_2}$ are continuous over $[t^*,T]$, then the functions $\displaystyle t \mapsto \int_0^t u^{\bar{b}_2}_s ds$ and $\displaystyle t \mapsto \int_0^t (u^{\bar{b}_2}_s- w^{\bar{b}_2}_s)^2 (\bar{x}_s^{MFG,\bar{b}_2} )^2 ds$ are continuous over $[t^*,T]$ and differentiable over $(t^*,T)$. We can apply the Mean Value theorem and deduce that there exists a time points $t_1$ depending on $b_2$ which satisfy $t^* < t_1 < T$ such that:
	\begin{IEEEeqnarray}{rCl}
		I_2 &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{t^*}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt \nonumber \\
		&=&  \frac{(u_{t_1}^{b_2} - w_{t_1}^{b_2})^2 e^{2(b_1 + \bar{b}_1)t_1} }{r + \bar{r}(1-\bar{s})^2}  \cdot  (b_2 + \bar{b}_2)^3 e^{ -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t_1} h_u(b_2,s) ds }.
	\label{eq:I2_b2_infity_Mean_Value}
	\end{IEEEeqnarray}	
	We know from equation (\ref{eq:ut_uniform_lower_bound_b2_infinity}) and (\ref{eq:ut_wt_upper_bound_b2_infty}) that for all $b_2 \geq \max \{b_2^{*,upper}, b_2^{*,lower} \}$ and all $t \in [0,T]$:
	\begin{equation*}
		\vert u_t^{b_2} - w_t^{b_2} \vert \leq \sup_{0 \leq t \leq T} \vert u_t^{b_2} \vert + \vert w_t^{b_2} \vert  \leq 2M
	\end{equation*}
	and 
	\begin{equation*}
		\int_0^{t_1} h_u(b_2,s) ds \geq \int_0^{t^*} h_u(b_2,s) ds \geq m_u(\epsilon_1) \cdot t^*.
	\end{equation*}
	Together with equation (\ref{eq:I2_b2_infity_Mean_Value}) give raise to
	\begin{equation*}
		I_2 \leq  \frac{4 M^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2)^3 e^{- \frac{2 t^*  m_u(\epsilon_1)}{r + \bar{r}(1-\bar{s})^2} (b_2 + \bar{b}_2) } = \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} 
	\end{equation*}
	where $\kappa_3 = \frac{4 M^2 e^{2(b_1 + \bar{b}_1) T} }{r + \bar{r}(1-\bar{s})^2} $ and $\kappa_4 := \kappa_4(\epsilon, \epsilon_1) =  \frac{2 t^*  m_u(\epsilon_1)}{r + \bar{r}(1-\bar{s})^2}$ are two positive constants independent of $b_2$. 	
	Hence, there exists $b_2^{*,I_2} := b_2^{*,I_2}(\epsilon, \epsilon_1) > \max \{b_2^{*,upper}, b_2^{*,lower} \}$ such that for all $b_2 \geq b_2^{*,I_2}$, 
	\begin{equation}
		I_2 \leq \kappa_3 (b_2 + \bar{b}_2)^3 e^{- \kappa_4 (b_2 + \bar{b}_2)} \leq \epsilon.
	\label{eq:I2_b2_infty}
	\end{equation}

	Let $\epsilon_1, \epsilon_2$ be two constants as follow:
	$$ \epsilon_1 = \frac{1}{2} \min \{ c_{\delta_u^{b_2 \to \infty}}, D^{u,b_2 \to \infty} \}\quad \text{and} \quad \epsilon_2 = \frac{1}{2} \min \{c_u, c_w\}.$$ Hence, 
	for any $\epsilon>0$, we can choose $t^*$ as shown in equation (\ref{eq:t^*_b2_infty}) so that for all $b_2 \geq b_2^*(\epsilon) := \max \{ b_2^{*,I_1}, b_2^{*,I_2}(\epsilon) \}$, the inequalities (\ref{eq:I1_b2_infty}) and (\ref{eq:I2_b2_infty}) yield
	\begin{equation*}
		\frac{\Delta SC}{SC^{MKV}} \leq \frac{I_1 + I_2}{(b_2 + \bar{b}_2) w_0^{b_2}} \leq \frac{ \epsilon + \epsilon }{h_w(b_2,0)} \leq \frac{2\epsilon}{c_w - \epsilon_2} 
	\end{equation*}
	Therefore, by letting $\epsilon \to 0$, we conclude that:
	\begin{equation*}
		\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0, 
	\end{equation*}
	which implies immediately
	$$ \lim_{b_2 \to \infty} PoA = 1.$$

\begin{comment}

@@

	\begin{comment}
	Idem, there exists 3 time points $t_7,t_8,t_9$ with $0<t_7<t_3<T$ and $0<t_8<t_9<t_3<T$ such that
	\begin{equation}
		v^{b_2}_{t_3} = \kappa_8 e^{-\kappa_7 b_2 h_\eta(b_2,t_7)} + \kappa_{10} e^{-\kappa_9 b_2 h_\eta(b_2,t_9)}
	\label{eq:v_{t_3}_b_2_expansion}
	\end{equation}
	where $ \displaystyle \kappa_7 = \frac{2t_3}{r+ \bar{r}}, \  \kappa_8 =Var(\xi) e^{2b_1 t_3}, \  \kappa_9 = \frac{2 (t_3 - t_8)}{r+ \bar{r}}, \  \kappa_{10}= \sigma^2 t_3 e^{2b_1 (t_3 - t_8)}$.
	%%%%%%% end{comment}
